Centering factor interactions

### 2014-07-30 _knitr-posts/2014-07-30-centering-interactions.Rmd
Publish centering post
Other trivial changes

---
layout: post
title: Centering factor interactions
subtitle: Why and how you must center interactions for model averaging
published: false
---

@@

Now, let's derive those same standard errors for the centered version. We'll start be extracting the standard errors and covariances of the coefficients. Then we'll combine them:

>>>>

---
layout: post
title: Centering factor interactions
subtitle: Why and how you must center interactions for model averaging
published: true
---

@@

Now, let's derive those same standard errors for the centered version. We'll start be extracting the standard errors and covariances of the coefficients. Then we'll combine them. Although we could do this more elegantly, we'll write it out in full to make it obvious what's happening.
